Information in recombination junctions can both compress and improve inferred tree sequences

### 2023-12-04 paper/writeup.tex
more notes

@@

@@

\subsection{Discrepancy Function}
% * How to measure agreement that includes haplotypes
% * Definition and Algorithm
% * Supp fig: runtime ~ # trees, samples
% * fig: how add edges rueduces discrepancy
%       - compare to Relate and tsinfer
% * Show: how add edges reduces discrepancy
% * THINK of a way to asynchronously computing discrepancy

@@

@@

\begin{figure}
    \caption{
        Summaries of correctly and incorrectly added spans
        ... as a function of number of samples?
        \label{fig:results_discrepancy}
    }
\end{figure}

>>>>

% Non-coalescing regions of dark matter in ARGs
% Can we find them? Are they useful in inference, dating? 
% Look, we can find them and they seem at least useful for compression.
% Also, here's a way of measuring agreement that takes this sort of thing into account,
%  which extends R-F to measure haplotypes

@@

\comment{idea: look at ratio of unary-to-not over time; does it change with
    selection? or modes of recombination?}

%%% OUTLINE
% Intro: haplotypes, unary bits of non-coalescing nodes, ARGS, etcetera
%    explain what tsinfer does to create unary regions
%    statement of problem
%    Yan: are breakpoints in true->simplify->extend the same as in original?
%   Fig 1: conceptual figure
%    Also IBD gets screwed up
% 
% Methods:
%   edge extend algorithm
%   discrepancy funciton algorithm
%   Fig 2: Conceptual figure for discrepancy
% 
% Results:
%   Fig 3:
%     (a) reduction in number of edges and (b) speed change
%
%   Fig 4:
%     Histograms of (a) total span added, (b) percent incorrect
%
%   Fig 5 and maybe 6: how it interacts with tsinfer
%     (a) summarize total matching and unmatching span (or maybe percent matching?)
%           across reps
%     (b) discrepancy per node against depth or time or number of subtended samples
%        describe percent span matched against true span or depth or something
%
%   Fig 7(?): compare IBD stats before/after
% 
% Supp:
%   S1: runtime
%%%

@@

\subsection{Discrepancy Function}
% * How to measure agreement that includes haplotypes
% * Definition and Algorithm
% * Supp fig: runtime ~ # trees, samples
% * fig: how add edges reduces discrepancy (RESULTS)
%       - compare to tsinfer
% * Show: how add edges reduces discrepancy (RESULTS)
% * THINK of a way to asynchronously computing discrepancy (???)

@@

\comment{
    Idea: look at statistical properties of unary regions:
    look at how much 'unary regions' there is in simulation
    and how much we can put back in,
    as a function of time.
}

@@
